---
title: "<br> Statistische Modellbildung II <br> Tutorium"
subtitle: ""
author: 'Fabio Votta <br><br> <a href="http://github.com/favstats"><i class="fa fa-github fa-fw"></i>&nbsp; favstats</a> <br> <a href="http://www.favstats.eu/"><i class="fa fa-address-card"></i>&nbsp; favstats.eu</a> <br> <a href="https://twitter.com/FabioFavusMaxim"> <i class="fa fa-twitter fa-fw"></i>&nbsp; @FabioFavusMaxim</a><br> <a href="mailto:fabio.votta@gmail.com"><i class="fa fa-paper-plane fa-fw"></i>&nbsp; fabio.votta@gmail.com</a> <br><br><br><br> 2018-17-09'
output: 
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      highlightLanguage: r
    includes:
      in_header: header.html      
    countIncrementalSlides: false
    css: xaringan-themer.css
---



    

```{r xaringan-themer, include = FALSE}
#library(xaringanthemer)
# mono_accent(base_color = "#252525", link_color	= "rgb(198, 219, 239)")
```

<style>
.onehundredtwenty {
  font-size: 120%;
   }

<style>
.ninety {
  font-size: 90%;
   }

.eightyfive {
  font-size: 85%;
   }
   
.eighty {
  font-size: 80%;
   }
   
.seventyfive {
  font-size: 75%;
   }
   
.seventy {
  font-size: 70%;
   }
</style>


```{r setup, echo = F, include=F}
# include=FALSE
options(htmltools.dir.version = FALSE)

pacman::p_load(tidyverse, xaringan)

knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

```


<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

.onehundredtwenty[

Research Question:

> What role does religiosity play in support for religious governance? 

]


---

class: inverse, center, middle


## Thank You!

Full Paper: <a href='http://www.academia.edu/36488238/Godly_Governance_A_Cross-National_Examination_of_Religious_Politics_in_Arab_Muslim-Majority_Countries'>Godly Governance</a>

Slides: <a href='https://godly-governance.netlify.com'>godly-governance.netlify.com </a>

Code and Data on <a href='https://github.com/favstats/GodlyGovernance'>GitHub</a>


---

## References



---

class: inverse, center, middle

## Appendix


